\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}
\usepackage{array}
\usepackage{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault} % Sets the font to Helvetica or similar sans-serif
\geometry{margin=0.8in, top=0.6in, bottom=0.6in}

% Header formatting
\pagestyle{empty}

% CV Body
\begin{document}

% Header
\begin{center}
    \textbf{\LARGE Bryan Tran} \\
    \vspace{2pt}
    \small Bonn, Germany • bryan.tran053@gmail.com • 0049 1573 7567116 • www.linkedin.com/in/btr-dev/
\end{center}
\vspace{8pt}
% Professional Summary
\section*{\normalsize PROFESSIONAL SUMMARY}
Experienced Software Engineer skilled in backend development, modular architecture, and cloud technologies. Proven track record in optimizing systems, modernizing legacy applications, and implementing scalable solutions. Seeking to bring technical expertise and innovative problem-solving abilities to a dynamic team.
% Technical Skills
\vspace{5pt}
\section*{\normalsize TECHNICAL SKILLS}
\begin{tabular}{ p{0.22\textwidth} p{0.75\textwidth} }
    \textbf{Languages:} & Python, Java, C\#, C++, JavaScript and more \\
    \textbf{Cloud Platforms:} & AWS (Lambda, EC2), Docker, Kubernetes and more \\
    \textbf{Tools:} & Git, GitLab CI/CD, IDA Pro, Fiddler, YAML and more \\
    \textbf{Frameworks:} & Camunda, SAFe, React.js and more \\
    \textbf{Other:} & Agile Methodologies, Data Structures, Machine Learning and more \\
\end{tabular}
% Experience
\vspace{5pt}
\section*{\normalsize EXPERIENCE}
\textbf{Software Engineer} \hfill \textbf{Deutsche Telekom, Bonn, Germany} \\
\textit{Oct 2023 – Present}
\begin{itemize}[leftmargin=*,itemsep=0.3pt,topsep=2pt]
    \item Modernized legacy codebase by replacing hardcoded elements with a dynamic structure, improving scalability.
    \item Transitioned monolithic workflows to a modular architecture using Camunda and Java.
    \item Developed a robust CI/CD pipeline with over 500 unit and integration tests.
\end{itemize}
\vspace{2pt}
\textbf{CTO and Developer} \hfill \textbf{Rhenus AI, Bonn, Germany} \\
\textit{Aug 2024 – Nov 2024}
\begin{itemize}[leftmargin=*,itemsep=0.3pt,topsep=2pt]
    \item Created a service tool leveraging AWS Transcribe for call transcription and AWS Bedrock for summarizing and categorizing conversations. This tool facilitates customer communication and root cause analysis.
    \item Developed an AI-based offer and tender tool that analyzes, translates, and summarizes documents, generating timelines and targeted summaries for different professional groups.
    \item Leading the development of a tool to automatically create new tender documents from historical data, utilizing RAGs and fine-tuning for optimal accuracy.
    \item Prioritized GDPR compliance and data protection by aligning all services with EU standards, reinforcing client trust in data security.
\end{itemize}
\vspace{2pt}
\textbf{Full Stack Developer} \hfill \textbf{Nutrio GmbH, Hildesheim, Germany} \\
\textit{Nov 2023 – Jan 2024}
\begin{itemize}[leftmargin=*,itemsep=0.3pt,topsep=2pt]
    \item Maintained backend and frontend systems on a C\#, React.js, and MariaDB stack.
    \item Improved user experience and system stability, prioritizing and resolving critical issues in a Kanban environment.
\end{itemize}
\vspace{2pt}
\textbf{Founder and Developer} \hfill \textbf{HelloBryan, Bonn, Germany} \\
\textit{Aug 2023 – Aug 2024}
\begin{itemize}[leftmargin=*,itemsep=0.3pt,topsep=2pt]
    \item Developed an AI-driven solution for SME support, leveraging AWS and dynamic web crawling for automation.
    \item Designed secure, scalable architectures using AWS services and implemented data processing algorithms.
\end{itemize}
\vspace{2pt}
\textbf{Freelance Software Engineer} \hfill \textbf{Remote} \\
\textit{2016 – Oct 2023}
\begin{itemize}[leftmargin=*,itemsep=0.3pt,topsep=2pt]
    \item Specialized in C++ for game security and exploit development, employing tools like IDA Pro and Fiddler.
    \item Delivered custom solutions and applied Agile practices, enhancing project outcomes for clients.
\end{itemize}
\vspace{2pt}
\textbf{Intern} \hfill \textbf{T-Systems MMS, Dresden, Germany (Remote)} \\
\textit{Aug 2021}
\begin{itemize}[leftmargin=*,itemsep=0.3pt,topsep=2pt]
    \item Learned the fundamentals of the LAMP stack, including setting up a web server and building a website with PHP and SQL backend.
    \item As an extracurricular project, installed Linux on a Nintendo Switch and hosted the server publicly, demonstrating a proactive approach to learning and exploring new technologies.
\end{itemize}
% Education
\vspace{5pt}
\section*{\normalsize EDUCATION}
\textbf{Bachelor’s Degree in Business Informatics} (in progress) \\
\textit{Fachhochschule der Wirtschaft (FHDW)} – Dual Study Program \\
Note: Currently considering a transition to focus fully on professional opportunities.
\end{document}
